Title

### 2024-05-13 paper/main.tex
udpates

\textbf{Para 5: Contributions}
\begin{enumerate}
	\item We present an effect size measure based on canonical correlations
		for mixed data that generalizes some of the commonly used
		effect size in special cases such as partial correlation
		coefficient for continuous variables, and Cram\'er's V for
		discrete variables.
	\item We also developed a web-based tool to help researches in
		constructing and testing and modifying their DAGs using CI tests and
		effect size measures.
\end{enumerate}

>>>>

\textbf{Para 5: Contributions}
\begin{enumerate}
	\item We present a procedure to construct and modify DAGs using domain
		knowledge.
	\item The presented procedure uses a (conditional) measure of
		association between variables. In the simple case of continuous
		or discrete variables, effect size measures can be used,
		however as no such measure exists for mixed data, we present
		one.
	\item Lastly, to assist researchers in using the DAG construction
		approach, we developed a web-based tool to help researches in
		constructing and modifying their DAGs.
\end{enumerate}
